--- 
title: "TFL book guide"
author: "Metrum Research Group"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output:
  tufte::tufte_handout: default
  tufte::tufte_html:
    toc: yes
    css: css/toc.css
  
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "A tutorial on using the Tables List and Figures (TFL) package"
---
```{r setup, echo=FALSE}
suppressMessages(library(texPreview))
rt=knitr::opts_knit$get('rmarkdown.pandoc.to')
fd=NULL 

if(rt%in%c("html", "html5", "s5", "slidy","slideous", "dzslides", "revealjs","md")){
  fd="_book/texPreview"
  if(!dir.exists(fd)) dir.create(fd,recursive = T)
}
```

# Preface {-}

The TFL package is an R package for creating tables, figures, and listings in a reproducible manner.

To compile this book you need to install **bookdown** from Github:

```{r one, eval=FALSE}
devtools::install_github("rstudio/bookdown")
```

Each Rmd file contains a chapter that explains sets of similar funcationalities as specified in the file name.

To compile this to PDF, you need to install XeLaTeX.

```{r two,include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

Load the Package
```{r three,echo=FALSE}
.libPaths("../script/lib")
suppressMessages({
                  library(tools)
                  library(TFL)
                  library(texPreview)
  })

fn.src=function(fn){
fn.rd=paste0('../TFL/man/',fn,'.Rd')
fn.hlp=paste0('_book/',fn,'Help.html')

tools::Rd2HTML(Rd = fn.rd,out = fn.hlp)
writeLines(paste0('<iframe width="100%" height="315" src="',fn.hlp,'" frameborder="0" allowfullscreen></iframe>'))
}
```

Load into the global enviornment data used in the tutorial
```{r four}
data("twoCmt")
```